\documentclass[10pt,a4paper,twoside]{article}
% Document Class
% Preamble
\usepackage[utf8]{inputenc}
% Setting the input encoding
\usepackage[english]{babel}
% The input language

% symbol is used for typing comments

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
% For including mathematical symbols

\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
% Used for shaping the size of the page

\author{Arun Prasaad Gunasekaran}
\title{Introduction to LaTeX}

\begin{document}
\maketitle
% Used for creating the title
Hello! This is my first LaTeX document! 

LaTeX files have many extensions!
This is a bullet list!
\begin{itemize}
\item .tex = TeX file. The core file and the most important file. All contents are written/typed within this file.
\item .bib bibliography files. It has the attributes and meta data (author's name, title, pages, abstract, year of publication ....)
\item .log Log file. It contains all the errors, warnings, execution messages, steps while compiling, etc.,
\item .aux .gz support files that come when a .tex file is executed.
\item .sty style format files. They contain TeX instructions and and formats to be included in the file.
\item .bst this is a style file for bibliography.
\item .toc this is a table of contents file
\item .cls class files.
\end{itemize}

This is a numbered list!
\begin{enumerate}
\item .tex = TeX file. The core file and the most important file. All contents are written/typed within this file.
\item .bib bibliography files. It has the attributes and meta data (author's name, title, pages, abstract, year of publication ....)
\item .log Log file. It contains all the errors, warnings, execution messages, steps while compiling, etc.,
\item .aux .gz support files that come when a .tex file is executed.
\item .sty style format files. They contain TeX instructions and and formats to be included in the file.
\item .bst this is a style file for bibliography.
\item .toc this is a table of contents file
\item .cls class files.
\end{enumerate}

Symbols:
Symbols in LaTeX are pre-assigned. So, you cannot use them directly.
Use backslash symbol to type the characters.
eg: \$ \% \&

Parenthesis:
Circular/Round brackets do not have any meaning. (). Square brackets have meaning in commands, but they can stand alone. [].

But! flower/curly brackets are reserved. You cannot print them directly! {}
To print them, use backslash \{ \}.

In commands, [] are used for filling optional arguments/instructions, whereas \{\} brackets are used for filling the command name.

use package commands are used for including special packages into the file (they add more features to the document)

The document structure is as follows

document class

use packages
definitions and macros
title page contents

document beginning

contents of the documents

document ending

ignored extras

\end{document}